---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# scoreMRDQ

<!-- badges: start -->
<!-- badges: end -->

The goal of scoreMRDQ is to convert the 59 responses from the Michigan Retinal Degeneration Questionnaire (MRDQ) to seven domain scores: Central Vision, Color Vision, Contrast Sensitivity, Scotopic Function, Photopic Peripheral Vision, Mesopic Peripheral Vision, and Photosensitivity.


## Installation

You can install the development version of scoreMRDQ from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("chrisandrewsphd/scoreMRDQ")
```

## Examples

### Example 1

This is a basic example which shows you how to score data from a single individual. `justme` is a data.frame with 15 variables and 1 row.  The 15 variables are the patient identifier followed by their 14 responses.

This is a basic example which shows you how to solve a common problem:

```{r example1}
library(scoreMRDQ)

justme <- read.table(
  text = "Me,0,0,0,0,0,0,0,0,1,1,1,0,0,0,1,1,1,2,0,0,0,0,1,1,1,0,0,0,0,1,0,0,1,0,0,1,0,0,1,0,0,1,0,0,1,0,0,2,1,1,0,0,0,0,0,2,0,0,0",
  sep = ",")
justme

scoreMRDQ(justme)
```

### Example 2
```{r example2}
library(scoreMRDQ)

justme <- read.table(
  text = "Me,0,0,0,0,0,0,0,0,1,1,1,0,0,0,1,1,1,2,0,0,0,0,1,1,1,0,0,0,0,1,0,0,1,0,0,1,0,0,1,0,0,1,0,0,1,0,0,2,1,1,0,0,0,0,0,2,0,0,0",
  sep = ",")
justyou <- data.frame(ID="You", matrix(nrow=1, sample(0:4, 59, TRUE)))
andyoutoo <- data.frame(ID="You 2", matrix(nrow=1, sample(0:4, 59, TRUE)))

names(justme) <- names(justyou) <- names(andyoutoo) <- 
  c("ID", sprintf("Q%0.2d", seq(59)))

justus <- rbind(justme, justyou, andyoutoo)
justus

scoreMRDQ(justus, verbose = 1)
```

The option `verbose = 1` provides some messaging during the execution of `scoreMRDQ()`.
